\documentclass[11pt, a4paper]{article}
% CHANGED: Added 'landscape' option and adjusted margins slightly
\usepackage[a4paper, landscape, top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{colortbl}
\usepackage{amssymb}

% --- FONTS ---
% NOTE: Ensure you have the Noto Sans font family installed, 
% or change this to a font available on your system (e.g., Arial).
\babelfont{rm}{Noto Sans}
\babelfont{sf}{Noto Sans}

% --- COLORS ---
\definecolor{primary}{RGB}{0, 51, 102}
\definecolor{lightgray}{RGB}{240, 240, 240}
\definecolor{headergray}{RGB}{200, 200, 200}

% --- TITLE FORMATTING ---
\titleformat{\section}
{\color{primary}\normalfont\Large\bfseries}
{\thesection}{1em}{}

\titleformat{\subsection}
{\color{primary}\normalfont\large\bfseries}
{\thesubsection}{1em}{}

% --- HYPERLINKS ---
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    filecolor=magenta,      
    urlcolor=blue,
}

% --- DOCUMENT INFO ---
\title{
    \vspace{1cm} % Reduced vertical space for landscape title page
    \Huge \textbf{Master Test Plan}\\
    \large White Rose Interiors WhatsApp Chatbot\\
    \normalsize COMP2171 Software Engineering Project
    \vspace{0.5cm}
}
\author{\textbf{Group 1} \\ University of the West Indies \\ COMP2171}
\date{April 10, 2026 \\ Version 2.6 (Landscape)}

\begin{document}

\maketitle
\thispagestyle{empty}
\vspace{1cm}

\begin{center}
    \begin{tabular}{|p{0.3\textwidth}|p{0.6\textwidth}|}
        \hline
        \rowcolor{lightgray} \textbf{Item} & \textbf{Details} \\
        \hline
        \textbf{Project Name} & White Rose Interiors Chatbot (COMP2171 Project) \\
        \hline
        \textbf{Document Type} & Master Test Plan (MTP) \\
        \hline
        \textbf{Version} & 2.6 (Landscape Orientation) \\
        \hline
        \textbf{Status} & \textbf{DRAFT} \\
        \hline
    \end{tabular}
\end{center}

\newpage
\tableofcontents
\newpage

% ---------------------------------------------------------------------

\section{Introduction}
This Master Test Plan (MTP) outlines strategy, resources, and procedures for testing the White Rose Interiors Chatbot. The system is a Node.js app using \texttt{whatsapp-web.js} and local JSON storage.

\subsection{Objectives}
\begin{itemize}
    \item Verify all functional requirements (UI, pricing, invoicing, dashboard, status, reminders, manage orders).
    \item Validate file-based storage integrity across updates (orders.json, cleaning\_supply.json, reminders.json).
    \item Ensure chatbot/dash respond within a few seconds under normal load and recover from invalid inputs.
\end{itemize}

\section{Test Environment}
\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|p{0.2\textwidth}|p{0.7\textwidth}|}
        \hline
        \rowcolor{headergray} \textbf{Component} & \textbf{Specification} \\
        \hline
        \textbf{Hardware} & Windows 10/11 or Server 2019+ \\
        \hline
        \textbf{Runtime} & Node.js v18+ \\
        \hline
        \textbf{Storage} & Local File System (orders.json, cleaning\_supply.json, reminders.json) \\
        \hline
        \textbf{Mobile} & 1 Android + 1 iOS for WhatsApp tests \\
        \hline
        \textbf{Browser} & Chrome/Edge for Admin Dashboard \\
        \hline
    \end{tabular}
    \caption{Test Environment Specifications}
\end{table}

\section{Entry \& Exit Criteria}
\subsection{Entry}
\begin{itemize}
    \item[$\square$] \texttt{server.js} starts without errors; WhatsApp client QR scanned and “Ready”.
    \item[$\square$] Baseline data present in \texttt{orders.json}, \texttt{cleaning\_supply.json}.
    \item[$\square$] Admin token obtainable via /api/login.
\end{itemize}

\subsection{Exit}
\begin{itemize}
    \item[$\square$] 100\% High-priority tests passed; no open High/Critical defects.
    \item[$\square$] PDFs generate on host FS; reminder logs written to \texttt{reminders.json}.
\end{itemize}

\newpage
\section{Test Case Execution Log}

% Redefine array stretch for execution tables
\renewcommand{\arraystretch}{1.3}

% UPDATED COLUMN WIDTHS FOR LANDSCAPE
% Total ~0.95 textwidth to ensure fit
% ID: 0.05 | Scenario: 0.12 | Steps: 0.22 | Expected: 0.20 | Status: 0.06 | Actual: 0.15 | Comments: 0.15
\subsection{Requirement 1: User Interface \& Flows}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    UI-01 & Main Menu & 1) Send “Hi”. & Shows: Goods/Services, Manage Orders, Get Order Status, Contact Support, FAQ. & & & \\ \hline

    UI-02 & Invalid Input & 1) From menu, send “99”. & Bot prompts to pick a listed option. & & & \\ \hline

    UI-03 & Cleaning Services & 1) Select Goods/Services → Cleaning Services. 2) Send “Need sofa cleaning”. & Bot replies that Cleaning Services are currently unavailable, notes the request, and state resets. & & & \\ \hline

    UI-04 & Cleaning Supplies & 1) Select Goods/Services → Cleaning Supplies. 2) Choose a category from cleaning\_supply.json poll. & Bot prompts “Please leave a message describing what you need,” then confirms receipt. & & & \\ \hline
\end{longtable}

\subsection{Requirement 2: Price Calculator}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    PC-01 & Blind Quote & 1) Select product. 2) Enter valid width/height. & Price matches grid + install; PDF estimate sent. & & & \\ \hline

    PC-02 & Invalid Dim & 1) Enter “-5”. & Bot rejects, asks for valid number. & & & \\ \hline

    PC-03 & Email Estimate & 1) Complete quote. 2) Choose “Email me”. & Email prompted, PDF emailed (or graceful failure message). & & & \\ \hline
\end{longtable}

\subsection{Requirement 3: Invoicing}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    INV-01 & Confirm Order & 1) From estimate, choose “Confirm Order”. & New order saved in \texttt{orders.json} with correct status (e.g., PENDING DELIVERY). & & & \\ \hline

    INV-02 & Email Failure & 1) Request email when SMTP unavailable. & Bot says “Could not send email…”, logs error. & & & \\ \hline
\end{longtable}

\subsection{Requirement 4: Admin Dashboard}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    AD-01 & Auth Negative (All Routes) & 1) Access /api/orders, /api/report, /api/status without token. & All protected endpoints return 401 Unauthorized. & & & \\ \hline

    AD-02 & Update Order & 1) Change status to READY. & Persisted to \texttt{orders.json}; notify ready sends WA msg. & & & \\ \hline

    AD-03 & Reminder UI & 1) Edit reminder time in table. & Picker stays open; saved time matches selection. & & & \\ \hline

    AD-04 & Filters/Report & 1) Apply text/status/date filters. 2) Download report. & Filters apply; CSV downloads successfully. & & & \\ \hline
\end{longtable}

\subsection{Requirement 5: Status Updates}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    ST-01 & Status Lookup & 1) Select “Get Order Status”. & Returns orders for caller’s phone only. & & & \\ \hline

    ST-02 & Status Change & 1) Admin updates status to "In Progress" or "Ready". & Customer receives WhatsApp notification; status persists in \texttt{orders.json}. & & & \\ \hline

    ST-03 & Job Completion & 1) Admin updates status to "Delivered" or "Picked Up". & Customer receives the status-change notification; status persists. & & & \\ \hline
\end{longtable}

\subsection{Requirement 6: Automated Reminders}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    REM-01 & Send Reminder & 1) Set reminderTime due soon. 2) Wait for scheduler. & WA reminder sent; \texttt{reminderSent}=true; \texttt{reminders.json} log written. & & & \\ \hline

    REM-02 & Reset Flag on Edit & 1) Reminder already sent (\texttt{true}). 2) Admin updates time. & \texttt{reminderSent} resets to \texttt{false} in JSON to allow re-send. & & & \\ \hline
\end{longtable}

\subsection{Requirement 7: Manage Orders (Self-Service)}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    MG-01 & Retrieve Booking & 1) Select “Manage Orders”. & Bot lists caller’s upcoming orders (max 10). & & & \\ \hline

    MG-02 & Reschedule & 1) Manage Orders → select order → Reschedule. & New date/time saved to \texttt{orders.json}; dashboard reflects update. & & & \\ \hline

    MG-03 & Cancel Booking & 1) Manage Orders → Cancel → confirm. & Order removed/updated; bot confirms; dashboard reflects change. & & & \\ \hline

    MG-04 & Invalid Selection & 1) In Manage Orders, choose invalid option. & Bot prompts to select a valid order/action. & & & \\ \hline
\end{longtable}

\subsection{Data Integrity \& Performance}
\begin{longtable}{|p{0.05\textwidth}|p{0.12\textwidth}|p{0.22\textwidth}|p{0.20\textwidth}|p{0.06\textwidth}|p{0.15\textwidth}|p{0.15\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{ID} & \textbf{Scenario} & \textbf{Steps} & \textbf{Expected} & \textbf{Stat} & \textbf{Actual Result} & \textbf{Comments} \\ \hline
    \endhead

    INT-01 & JSON Integrity & 1) Corrupt cleaning\_supply.json. & Bot handles error/logs; no crash (graceful fallback). & & & \\ \hline

    INT-02 & Order JSON Corrupt & 1) Manually corrupt \texttt{orders.json} (bad syntax). 2) Restart. & Error logged; service does not crash, but data load fails gracefully (no backup expected). & & & \\ \hline

    PERF-01 & Response SLA & 1) Send 5 rapid messages. & Replies within a few seconds each under normal load. & & & \\ \hline
\end{longtable}

\newpage
\section{Requirements Traceability Matrix}

\renewcommand{\arraystretch}{1.4}
\begin{longtable}{|p{0.25\textwidth}|p{0.70\textwidth}|}
    \hline
    \rowcolor{headergray} \textbf{Requirement ID} & \textbf{Associated Test Cases} \\ \hline

    \textbf{Req 1: User Interface} & UI-01, UI-02, UI-03, UI-04 \\ \hline
    1.1 Display service options & UI-01 \\ \hline
    1.2 Select options via number/keyword & UI-01, UI-04 \\ \hline
    1.3 Invalid input detection & UI-02, MG-04 \\ \hline
    1.4 Correct next–step routing & UI-03, UI-04 \\ \hline

    \textbf{Req 2: Price Calculator} & PC-01, PC-02, PC-03 \\ \hline
    2.1 Generate estimate & PC-01 \\ \hline
    2.2 Send quotation via WA/email & PC-01, PC-03 \\ \hline

    \textbf{Req 3: Invoice Generation} & INV-01, INV-02 \\ \hline
    3.1 Generate invoice & INV-01 \\ \hline
    3.2 Store invoice/order details & INV-01 \\ \hline
    3.3 Email invoice & INV-01, INV-02 \\ \hline

    \textbf{Req 4: Admin Dashboard} & AD-01, AD-02, AD-03, AD-04 \\ \hline
    4.1 Generate report & AD-04 \\ \hline
    4.2 Filter dashboard data & AD-04 \\ \hline
    4.3 Display totals, unresolved tickets & AD-04 \\ \hline

    \textbf{Req 5: Status Updates} & ST-01, ST-02, ST-03 \\ \hline
    5.1 Query status & ST-01 \\ \hline
    5.2 Retrieve job status & ST-01 \\ \hline
    5.3 Proactive updates & ST-02 \\ \hline
    5.4 Final message after completion & ST-03 \\ \hline

    \textbf{Req 6: Automated Reminders} & REM-01, REM-02 \\ \hline
    6.1 Scan upcoming appointments & REM-01 \\ \hline
    6.2 Send reminder messages & REM-01 \\ \hline
    6.3 Confirm/reschedule options & REM-01, MG-02 \\ \hline
    6.4 Log reminder sent & REM-01, REM-02 \\ \hline

    \textbf{Req 7: Manage Orders} & MG-01, MG-02, MG-03, MG-04 \\ \hline
    7.1 Retrieve upcoming appointments & MG-01 \\ \hline
    7.2 Authenticate by phone number & MG-01 \\ \hline
    7.3 Present reschedule/cancel options & MG-02, MG-03 \\ \hline
    7.4 Reschedule flow & MG-02 \\ \hline
    7.5 Cancel flow & MG-03 \\ \hline

    \textbf{Non-functional: Performance} & PERF-01 \\ \hline
    \textbf{Non-functional: Data Integrity} & INT-01, INT-02 \\ \hline

\end{longtable}

\section{Defect Report Template}
\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|p{0.10\textwidth}|p{0.10\textwidth}|p{0.05\textwidth}|p{0.65\textwidth}|}
        \hline
        \rowcolor{headergray} \textbf{Defect ID} & \textbf{Test ID} & \textbf{Sev} & \textbf{Description of Failure} \\
        \hline
        & & & \\
        \hline
        & & & \\
        \hline
    \end{tabular}
\end{table}

\section{Approvals}
\vspace{1cm}
\begin{tabular}{p{0.4\textwidth} p{0.5\textwidth}}
    \textbf{QA Lead:} & \hrulefill \\
    & \small{(Signature / Date)} \\[1cm]
    
    \textbf{Developer Lead:} & \hrulefill \\
    & \small{(Patrick Marsden)} \\[1cm]
    
    \textbf{Client Representative:} & \hrulefill \\
    & \small{(White Rose Interiors)} \\
\end{tabular}

\end{document}
